Data Processing

### 2024-03-15 R/processing-code/processingfile-v1.qmd
Fix on loading data

```{r}
library(readxl)
rawdata <- read_excel("~/Desktop/MADA-course/Nyamuranga-MADA-project/data/raw-data/elife-87430-data1-v1.xlsx")
```

@@

```{r}
library(readxl)

range_to_read <- "A4:M24"

# Read the Excel file into a data frame
figure1a <- read_excel("~/Desktop/MADA-course/Nyamuranga-MADA-project/data/raw-data/elife-87430-data1-v1.xlsx", sheet = "Figure 1-suppl figure 1", range = range_to_read)

summary(figure1a)
```

>>>>

```{r}
# path to data
# note the use of the here() package and not absolute paths
data_location <- here::here("data/raw-data/elife-87430-data1-v1.xlsx")
rawdata <- readxl::read_excel(data_location)
```

@@

```{r}
range_to_read <- "A4:M24"

figure1a <- readxl::read_excel(data_location, sheet ="Figure 1-suppl figure 1" , range = range_to_read)

print(figure1a)
```
